### 2024-09-14 actuarial.qmd
20240913 - experts

Humans are typically given no feedback on their judgments.
To improve accuracy of judgments, it is important for feedback to be clear, consistent, and timely.

>>>>

Humans are typically given no feedback on their judgments.
To improve accuracy of judgments, it is important for feedback to be clear, consistent, and timely.
Intuition is a form of recognition-based judgment (i.e., recognizing cues that provide access to information in memory).
Development of strong intuition depends on the quality and speed of feedback, in addition to having adequate opportunities to practice [i.e., sufficient opportunities to learn the cues; @Kahneman2011].
The quality and speed of the feedback tend to benefit anesthesiologists who often quickly learn the results of their actions.
By contrast, radiologists tend not to receive quality feedback about the accuracy of their diagnoses, including their [false-positive](#sec-falsePositive) and [false-negative](#sec-falseNegative) decisions [@Kahneman2011].

In general, many so-called experts are "pseudo-experts" who do not know the boundaries of their competence—that is, they do not know what they do not know; they have the illusion of validity of their predictions and are [overconfident](#sec-cognitiveBiasesOverconfidence) about their predictions [@Kahneman2011].
Yet, many people arrogantly proclaim to have predictive powers, including in low-validity environments such as fantasy football.
Indeed, people are more likely to watch a show if the pundits are opinionated, clear, and (overly) confident, because they are more entertaining [even though they less to be less accurate than individuals who thinking is more complex and less decisive; @Kahneman2011].
True experts know their limits in terms of knowledge and ability to predict.

Intuitions tend to be skilled when a) the environment is regular and predictable, and b) there is opportunity to learn the regularities, cues, and contingencies through extensive practice [@Kahneman2011].
Example domains that meet these conditions supporting intuition include activities such as chess, bridge, and poker, and occupations such as medical providers, athletes, and firefighters.
By contrast, fantasy football and other domains such as stock-picking, clinical psychology, and other long-terms forecasts are low-validity environments that are irregular and unpredictable.
In environments that do not have stable regularities, intuition cannot be trusted [@Kahneman2011].
